\cleardoublepage
%\pagebreak
\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgements}
\chapter*{Acknowledgments}
I would like to express our deep-felt appreciation and gratitude to \textbf{Mrs. E Padmalatha}, my project guide, for her skilful guidance, constant supervision, timely suggestion, keen interest and encouragement in completing the individual seminar within the stipulated time.
\par
I wish to express my gratitude to \textbf{Dr. T Sridevi} and \textbf{Mr. J Shiva Sai}, Project Coordinators, who have shown keen interest and even rendered their valuable time and guidance in terms of suggestions and encouragement.
\par
I am honoured to express my profound sense of gratitude to \textbf{Dr. M Swamy Das}, Head of Department, CSE, who has served as a host of valuable corrections and for providing me time and amenities to complete this project.
\par
I gratefully express my thanks to \textbf{Dr. P Ravinder Reddy}, Principal of our college and the management of CHAITANYA BHARATHI INSTITUTE OF TECHNOLOGY for providing excellent academic and learning environment in the college.
\par
I wish to express my heartfelt gratitude to the Members of Staff and all others who helped me in bringing up my project. I would also like to thank the Lab assistants and Programmers for helping me through my project.
\\
\begin{flushright}
\begin{comment}\textbf{Karedla Anantha Sashi Sekhar}\\\textbf{160114733091}\\\end{comment}
\textbf{Dasarada Ram Reddy Mudiam}\\\textbf{160114733092}
\end{flushright}
\newpage
