\cleardoublepage
%\pagebreak
\phantomsection
\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{99}
\bibitem{ovif}
Gao, Yuan and Liu, Hong and Sun, Xiaohu and Wang, Can and Liu, Yi. \emph{Violence Detection Using Oriented Violent Flows},Key Laboratory of Machine Perception, Shenzhen Graduate School, Peking University, Beijing 100871, China. Image Vision Comput, April 2016

\bibitem{hassner}
T.~Hassner, Y.~Itcher, O.~Kliper~Gross. \emph{Violent Flows: Real-Time Detection of Violent Crowd Behavior},3rd IEEE International Workshop on Socially Intelligent Surveillance and Monitoring (SISM) at the IEEE Conf. on Computer Vision and Pattern Recognition (CVPR),June 2012

\bibitem{liu}
Ce.~Liu. \emph{Beyond Pixels: Exploring New Representations and Applications for Motion Analysis},Massachusetts Institute of Technology,Ph.D. Thesis,2009

\bibitem{bob}
Anjos, Andr\'e AND El Shafey, Laurent AND Wallace, Roy AND G\"unther, Manuel AND McCool, Christopher AND Marcel, S\'ebastien. \emph{Bob: a free signal processing and machine learning toolbox for researchers},20th ACM Conference on Multimedia Systems (ACMMM), Nara Japan, 2012s

\bibitem{fight}
Eugene Yujun Fu, Hong Va Leong, Grace Ngai, Stephen Chan \emph{Automatic Fight Detection in Surveillance Videos} 2016

\bibitem{crowd}
Andrea Pennisi, Domenico D. Bloisi, Luca Iocchi \emph{Online real-time crowd behaviour detection in video sequences} 2015

\bibitem{keras}
Chollet, Fran\c{c}ois and others. \emph{Keras}, 2015. Source available at\url{https://keras.io}

\bibitem{opencv}
Itseez. \emph{Open Source Computer Vision Library}, 2015. Source available at \url{https://github.com/itseez/opencv}

\bibitem{tensorflow}
Martín Abadi, Ashish Agarwal, Paul Barham, Eugene Brevdo,
Zhifeng Chen, Craig Citro, Greg S. Corrado, Andy Davis,
Jeffrey Dean, Matthieu Devin, Sanjay Ghemawat, Ian Goodfellow,
Andrew Harp, Geoffrey Irving, Michael Isard, Rafal Jozefowicz, Yangqing Jia,
Lukasz Kaiser, Manjunath Kudlur, Josh Levenberg, Dan Mané, Mike Schuster,
Rajat Monga, Sherry Moore, Derek Murray, Chris Olah, Jonathon Shlens,
Benoit Steiner, Ilya Sutskever, Kunal Talwar, Paul Tucker,
Vincent Vanhoucke, Vijay Vasudevan, Fernanda Viégas,
Oriol Vinyals, Pete Warden, Martin Wattenberg, Martin Wicke,
Yuan Yu, and Xiaoqiang Zheng.
\emph{TensorFlow: Large-scale machine learning on heterogeneous systems}, 2015. Source available at \url{ https://www.tensorflow.org}

\bibitem{video}
Video: \url{https://en.wikipedia.org/wiki/Video}

\bibitem{OpticalFlow}
Optical Flow: \url{https://en.wikipedia.org/wiki/Optical_flow}

\bibitem{CrowdAnalysis}
Crowd Analysis: \url{https://en.wikipedia.org/wiki/Crowd_analysis}

\bibitem{unix}
Unix: \url{https://en.wikipedia.org/wiki/Unix}

\bibitem{Python}
Python: \url{https://en.wikipedia.org/wiki/Python_(programming_language)}





\end{thebibliography}
